% Use the moderncv class.
\documentclass[11pt,a4paper,sans]{moderncv}

% Prevent hyphenation on word wrap.
\usepackage[none]{hyphenat}

% Character encoding
\usepackage[utf8]{inputenc}

% moderncv themes
% style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 
% 'fancy'
\moderncvstyle{classic}
% color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 
% 'orange', 'purple' and 'red'
\moderncvcolor{grey}
% To set the default font; use '\sfdefault' for the default sans serif font,
% '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}
% Uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}


% Page style
% Set page margins
\usepackage[scale=0.9]{geometry}
% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}
% For the 'classic' style, if you want to force the width allocated to your
% name and avoid line breaks. be careful though, the length is normally
% calculated to avoid any overlap with your personal info; use this at your own
% typographical risks...
%\setlength{\makecvtitlenamewidth}{10cm}

% Personal data
\name{Kevin}{Laude}
\title{Developer, IT Architect, Community Evangelist}
\address{Ask me}{for my address}
\phone[mobile]{Ask me}
\email{nerfyoda@gmail.com}
\social[github]{klaude}
\social[linkedin]{kevinlaude}

\begin{document}
    % Personal Data
    \makecvtitle

    % Knowledge
    \section{Knowledge}
        \cvitem{Languages}{PHP, HTML, SQL, Perl, Bash, Javascript, CSS, Python, Ruby, Expect, LaTeX, C\#.NET, vb.NET, Pascal, m68k assembly}
        \cvitem{Linux}{Red Hat Exterprise Linux, CentOS, Fedora, Cloud Linux, Debian, Ubuntu, Gentoo, Arch}
        \cvitem{UNIX}{OS X, FreeBSD, OpenBSD, iOS}
        \cvitem{Other OS}{Microsoft Windows, Cisco IOS}
        \cvitem{Editors}{vim, Sublime Text, Eclipse, Phpstorm, Visual Studio}
        \cvitem{Frameworks}{jQuery, YUI, Zend Framework, Symfony, Laravel, Slim, Composer, Selenium}
        \cvitem{Data}{MySQL, SQLite, Oracle}
        \cvitem{Protocols}{HTTP, SSL, SSH, FTP, SMTP, DNS, IMAP, POP3, TCP/IP, REST, SOAP, XML-RPC, LDAP, Active Directory}
        \cvitem{Hosting}{cPanel, Parallels, Google hosted apps, Apache, ProFTPd, Pureftpd, Sendmail, Exim, Nginx, Lighttpd, IIS, Courier, ClamAV, Spamassassin, Icecast, Teamspeak}
        \cvitem{Virtualization}{QEMU/KVM, Xen, Virtualbox, FreeBSD jails, VMware Fusion, Parallels, OpenVZ}
        \cvitem{Programs}{git, subversion, PHPUnit, Microsoft Office, LibreOffice, JIRA, FogBugz, Jenkins, dotProject, Wordpress, MediaWiki, vBulletin}
        \cvitem{Multimedia}{Adobe Photoshop, Adobe Illustrator, GIMP, iMovie, GarageBand, Ableton Live, ImageMagick}
        \cvitem{Concepts}{PHP, Perl, and Python best practices, LAMP stack, development methodologies and best practices, remote API design and development, code design and deployment, MVC architecture, AJAX, systems and data security, functional and unit testing, datacenter and hardware management, local, wireless, and WAN networking, project management, gaming server administration}
        \cvitem{Soft Skills}{Verbal, visual, and written communication, authoring documentation, direct client interaction, pre-sales engineering, conference speaking, clear \& concise troubleshooting, leading development \& support teams, corporate social media interaction, trade-show staffing, coordinating repairs}

    % Experience
    \section{Experience}
        % Cinsay
        \cventry{2013}{Lead PHP Engineer}{Cinsay, Inc.}{Dallas, TX/Austin, TX}{\httplink[http://cinsay.com/]{cinsay.com}}{Performed PHP web development in an SOA environment
        \begin{itemize}
            \item Acted as lead and primary developer with a small team on an administrative website project, producing the site ahead of schedule including features planned for later releases.
            \item Assisted the development team in product launches.
            \item Assigned level of effort and developers to new issues.
            \item Consulted with senior and project management on new task and project technical requirements.
        \end{itemize}}

        % SingleHop
        \cventry{2012--2013}{Lead Developer}{SingleHop LLC}{Chicago, IL}{\httplink[http://singlehop.com/]{singlehop.com}}{Implemented development environments and standards
        \begin{itemize}
            \item Created scalable and maintainable per-project and per-developer development environments for all SingleHop web-based projects.
            \item Served as a point of contact for development and support escalations.
            \item Assisted the development team in maintaining current projects.
        \end{itemize}}

        % cPanel
        \cventry{2011--2012}{Quality Assurance Analyst}{cPanel, Inc.}{Houston, TX}{\httplink[http://cpanel.net/]{cpanel.net}}{Performed functional product testing of the largest hosting automation platform.\newline{Built a testing suite framework in Perl.}
        \begin{itemize}
            \item Ran manual tests against cPanel and WHM builds on numerous 32 and 64-bit Linux distributions to verify functionality on a per-feature or per-issue report basis.
            \item Created and maintained a number of automated browser based product tests using in-house and the Selenium framework automated testing suites.
            \item Designed, developed, and maintained a robust MVC framework capable of handling multiple dispatched requests and multiple projects, each with controllers, view redirects, dispatching based on "fake folders", and error handling in Perl 5.10. This framework is used by Quality Assurance developers to generate dynamic web pages within a custom testing suite.
            \item Implemented test cases and test plans in the aforementioned MVC framework.
            \item Provided the visual design, consistent look and feel, and user experience for all pages built in this framework.
        \end{itemize}}

        % SoftLayer
        \cventry{2007--2010}{Senior Application Developer / API Evangelist}{SoftLayer Technologies, Inc.}{Dallas, TX}{\httplink[http://softlayer.com/]{softlayer.com}}{Acted as the primary point of contact and one of the principle developers of the SoftLayer SOAP, XML-RPC, and REST APIs
        \begin{itemize}
            \item  Designed, built, and maintained a PHPDoc based syntax for maintaining public-facing documentation within code files, allowing individual developers to write technical documentation as a part of the development process. Documentation was periodically read from source code, formatted, and published to a public-facing API documentation wiki.
            \item Created and managed SoftLayer's documentation wiki and public-facing, open-source code project at \httplink{github.com/softlayer}.
            \item Developed PHP, Perl, and Python bindings for the SoftLayer API.
            \item Developed Stratos, a web-based portal based on Zend Framework 1 and SoftLayer's PHP API bindings that controls SoftLayer servers and services that users can install into any PHP-ready web server.
            \item Authored sample API usage scripts for customers written in C\#, Perl, PHP, Python, and vb.NET.
            \item Re-implemented SoftLayer's support ticketing system in SoftLayer's custom-built framework while implementing a number of application and presentation layer fixes that significantly reduced page load time and application server load.
            \item Worked numerous other development projects as a part of the SoftLayer development team. Highlights include bandwidth polling and display maintenance, modifying the user password and role system,  implementing the SoftLayer website as a project in SoftLayer's internal framework, and designing a version of the SoftLayer mobile portal optimized for mobile webkit-based browsers.
            \item Assisted in Android application development, providing icons and other static graphics.
            \item Represented SoftLayer at numerous industry and technology conferences and trade shows, serving as an on-site technical contact and meeting with customers, vendors, and prospective clients. I've spoken at HostingCon 2009, the hosting industry's premier trade show and cPanel Conference 2009, demonstrating a home-built proof of concept that enables cPanel to call an external API.
            \item Served as a 24/7 point of escalation for SoftLayer API and development issues in both pre and post-sales roles.
            \item Authored and edited posts in the SoftLayer Developer Network blog.
            \item Administered, moderated and maintained SoftLayer's customer forums and unofficial IRC channel.
        \end{itemize}}

        % The Planet - Insomnia365
        \cventry{2004--2007}{Application Developer}{The Planet Internet Services}{Dallas, TX}{\httplink[http://theplanet.com/]{theplanet.com}}{Designed, managed, and maintained a product line focused on the dedicated game server hosting industry.
        \begin{itemize}
            \item As part of a small development team I helped design, develop, and maintain Cortex, a web-based game server control panel. Designed as a server installable application, Cortex gave end users a web interface to on-line game server installation, configuration and administration. Primary duties included base system design, UI design, game server integration, and Linux OS integration. Additional duties include handling Cortex support via on-call phone and ticket escalations and creation and maintenance of the Cortex user manual.
            \item The Cortex project was an integral portion to The Planet's game hosting entity, Insomnia365. Duties for insomnia365 included moderating Insomnia365's IRC channel, working with strategic partners to provide stable game hosting platforms, and assisting in defining Insomnia365's product offerings.
            \item As a strategic partner I worked for Insomnia365 at the bi-yearly Cyberathlete Professional League professional gaming tournaments. Duties included network setup and maintenance, end user system troubleshooting, game server administration, and staffing a marketing booth.
            \item As a member of The Planet's development team I integrated 3rd party software into The Planet's internal systems, designed user interfaces, added efficiencies by implementing AJAX calls, and performed numerous development one-off projects for The Planet's support portal and departments.
        \end{itemize}}

        % The Planet - NOC Technician
        \cventry{2003--2004}{Network Operations Center Technician}{The Planet Internet Services}{Dallas, TX}{\httplink[http://theplanet.com/]{theplanet.com}}{Provided support and maintenance for an enterprise-class datacenter facility.
        \begin{itemize}
            \item Performed physical maintenance of a 60,000 sq. ft. secure datacenter. Monitored customer and internal equipment for network and physical faults. Provided ticket, phone, email, and personal support for enterprise and entry level dedicated servers. Levels of support ranged from hardware and network to operating system and application troubleshooting.
            \item Duties also included administration and moderation of The Planet's customer forums.
        \end{itemize}}

    % Education
    \section{Education}
        \cventry{2002--2003}{The University of Texas at Dallas}{Dallas,  TX}{Computer Science, Electrical Engineering}{\textit{GPA: 3.53}}{}
        \cventry{1996--2000}{The University of Texas at Austin}{Austin, TX}{Computer Science, Visual Design, Studio Art}{\textit{GPA: 3.0, Major: 3.875}}{}
        \cventry{1995}{The School of the Art Institute}{Chicago, IL}{Studio Art}{}{}

    % Projects
    \section{Projects}
        \cvitem{Occupy Houston}{Provided online logistics and website, Twitter, and Facebook content for a localized Occupy movement in Houston, TX. Managed the web and media teams, coordinating publishing for political actions and handling online content for other working groups within the Occupy Houston organization. Maintained the movement's local Internet connectivity. Organized political marches with other Occupy Houston members and city officials.\newline
        \newline
        Currently hosting the occupyhouston.org website and maintaining access to email accounts, mailing lists, and calendaring provided by Google Hosted Apps.\newline
        \newline
        {\httplink[http://www.occupyhouston.org/]{www.occupyhouston.org}}}
        \cvitem{The Jedi Academy}{Designed the visual layout and hand coded the website for an online video game school in PHP utilizing a MySQL backend. This site features an interactive forum, comments system, interactive class schedule, student application and testing queues, news posting system, cookie and user authentication based login with access to personal user profiles, and profile security levels for administrative purposes, and the means to manage all of these options through administrative functions.\newline
        \newline
        Currently maintaining the www.thejediacademy.net website and administering virtual mailboxes, FTP hosting, audio broadcasting, and VOIP services for academy members.\newline
        \newline
        {\httplink[http://www.thejediacademy.net/]{www.thejediacademy.net}}}

    % Interests
    \section{Interests}
        \cvlistitem{Coffee}
        \cvlistitem{Keeping up to date on technology trends}
        \cvlistitem{Star Wars trivia}
        \cvlistitem{Guitar and ukulele}
        \cvlistitem{Pencil, charcoal, and ink sketching}

\end{document}
